---
title: "R Markdown with Other Engines"
author: "Yingqi Jing"
date: "`r format(Sys.time(), '%B %e, %Y')`"
header-includes:
  - \usepackage{textcomp}
  - \renewcommand{\thefigure}{S\arabic{figure}}
  - \renewcommand{\thetable}{S\arabic{table}}
  - \renewcommand{\thesection}{S\arabic{section}}
  - \renewcommand{\thesubsection}{S\arabic{section}.\arabic{subsection}}
  - \usepackage{tocloft}
  - \settowidth{\cftsecnumwidth}{S10x}
output: 
  pdf_document:
   fig_crop: true
   fig_caption: true
   latex_engine: xelatex
   toc: true
   toc_depth: 4
   number_section: true
   pandoc_args: ["--variable=lof","--variable=lot","--bibliography=/Users/jakejing/switchdrive/bib/references.bib", "--csl=/Users/jakejing/switchdrive/bib/unified-style-linguistics.csl"]
---

```{r setup, include=FALSE}
library(knitr)
library(ggplot2)
library(Rcpp) # for running cpp code in R
library(rstan) # for running stan code in R
library(reticulate) # for running python code in R
use_python('/usr/local/bin/python3', required = T) #set the python engine path
library(JuliaCall) # for running julia code in R
knit_hooks$set(crop = hook_pdfcrop, pars = function(before, options, envir) {if(before) {par(family=my.font)} else NULL})
opts_chunk$set(fig.path='figures/',
               dev = 'cairo_pdf', dev.args=list(bg='transparent'), # or quartz_pdf (for lattice)
               fig.height = 5,
               fig.width = 6,
               #engine.path = list(julia = '/Applications/Julia-1.3.app/Contents/Resources/julia/bin/'), # do not use engine path, it does not allow variable inheritance across chunks
               # python.reticulate = T,  # seem to be not necessary
               message = F,
               warning = F,
               autodep=T,
               cache.comments=F,
               crop=T,
               comment=NA,
               pars=T)
# graphics setup:
my.font = 'Helvetica'
# ggplot
theme_set(theme_bw(base_size = 24) +
            theme(text = element_text(family = my.font),
                  plot.background = element_rect(fill = "transparent", colour = NA)))

options(width=180)
```

\clearpage

R Markdown
======

Including Plots
----------

You can also embed plots, for example:

```{r pressure, echo=F, cache=T, fig.height = 4, fig.width = 5, fig.cap="Relationship between temperature and presure"}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r print varaiable, include=FALSE}
#  one chunk of code, but it will still be evaluated
x = 1+1
print(x)
```


### subsubsection

```{r cars, results='hide'}
summary(cars)
```

Python code chunk
======

Access objects between R and Python
----------

### py$x in R chunk vs. r.x in python chunk

- Access to objects created within Python chunks from R using the py object (e.g. py$x would access an x variable created within Python from R).

- Access to objects created within R chunks from Python using the r object (e.g. r.x would access to x variable created within R from Python)


```{python}
x = 'hello, python world!'
print(x.split(' '))
```


```{r}
# source the python script
# source_python("flights.py")
# py_install("pandas")

# using py$x to inherit a python object 
newvar = paste(py$x, "add R")
print(newvar)
```


```{python}
# using r.x to access an R object
print(r.newvar)
```


C++ code chunk
=======

```{Rcpp, define a function}
#include <Rcpp.h>
using namespace Rcpp;
// [[Rcpp::export]]
NumericVector timesTwo(NumericVector x) {
  return x * 2;
}
```

```{r}
out = timesTwo(10) # test function in R chunk or console
out
```

Julia code chunk
=======

It seems that Julia code can be inherited across different chunks. This is one big advantage!

<!-- ```{julia} -->
<!-- # the semicolon holds printing -->
<!-- list1 = ["Julia", "is fast!"]; -->
<!-- println(list1) -->
<!-- mystring = "my test sting for julia" -->
<!-- ``` -->

<!-- ```{julia} -->
<!-- mystringnew = "$(mystring) new"; -->
<!-- println(mystringnew) -->
<!-- ``` -->


Bash script
========

**Note:** Bash script in one chunk **cannot** be inherited by another chunk!

```{bash}
echo "Hello Bash"
```

```{bash}
FILE='bash_name'
echo $FILE
```

Stan code chunk
==========

We can assign the stan code to a variable ($model1$), and can use this later in the `R` code chunk. 

<!-- ```{stan, output.var="model1"} -->
<!-- parameters { -->
<!--   real y[2]; -->
<!-- } -->
<!-- model { -->
<!--   y[1] ~ normal(0, 1); -->
<!--   y[2] ~ double_exponential(0, 2); -->
<!-- } -->
<!-- ``` -->

<!-- ```{r, message=FALSE} -->
<!-- fit <- sampling(model1, chains = 1) -->
<!-- print(fit) -->
<!-- ``` -->
