---
title: | 
       | Rmarkdown template for slides
       | 
author: "Yingqi Jing"
institute: "\\normalsize Department of Comparative Language Science"
# titlegraphic: ./logo/uzh.pdf
# logo: ./logo/uzh.pdf
fontsize: 11pt
date: "`r format(Sys.time(), '%B %e, %Y')`"
output: 
  beamer_presentation: # powerpoint_presentation
    template: /Users/jakejing/git/knitr-markdown-engines/templates/svm-latex-beamer.tex
    # theme: "gc3"
    keep_tex: true
    latex_engine: xelatex # pdflatex also works here
    # dev: cairo_pdf # I typically comment this out  if latex_engine: pdflatex
    # slide_level: 3 # it will create a separate page for each section
    pandoc_args: ["--bibliography=/Users/jakejing/switchdrive/bib/references.bib", "--csl=/Users/jakejing/switchdrive/bib/unified-style-linguistics.csl"]
header-includes:
  - \usepackage{textpos}
  - \addtobeamertemplate{title page}{}{\begin{textblock*}{40mm}(.01\textwidth,-7cm) \includegraphics[width=3.5cm, height=2.5cm]{/Users/jakejing/git/knitr-markdown-engines/logo/uzh.pdf} \end{textblock*}}
  # - \addtobeamertemplate{title page}{\includegraphics[width=4cm, height=3cm]{./logo/uzh.pdf}\par}{}
  # - \addtobeamertemplate{title page}{\centering \includegraphics{./logo/uzh.pdf}\par TEXT}{}
#   - \titlegraphic{\centering \includegraphics{./logo/uzh.pdf}}
#   - \pretitle{\begin{center}
#     \includegraphics[width=2in,height=2in]{logo/uzh.pdf}\LARGE\\}
#   - \posttitle{\end{center}}
make149: true
mainfont: "Times" # Try out some font options if xelatex
titlefont: "Times" # Try out some font options if xelatex
---

```{r setup, include=FALSE}
library(knitr)
library(ggplot2)
library(kableExtra) # kable
knit_hooks$set(crop = hook_pdfcrop, pars = function(before, options, envir) {if(before) {par(family=my.font)} else NULL})
opts_chunk$set(fig.path='figures/',
               dev = 'cairo_pdf', dev.args=list(bg='transparent'), # or quartz_pdf (for lattice)
               fig.height = 5, fig.width = 6,
               # engine.path = list(python = '/usr/local/bin/python3'),
               # python.reticulate = T, # not necessary, if use_python() is used above
               message = F,
               warning = F,
               autodep=T,
               cache.comments=F,
               crop=T,
               comment=NA,
               pars=T)
# graphics setup:
my.font = 'Helvetica'
```


# R Markdown

You can include **Knit** markdown as *normal*^[A footnote].

And there is a lot of variety about appearance and styles [@Osborne2006]. If you want to change how the presentation looks like, you can choose any of the next theme options: `default`, `simple`, `sky`, `beige`, `serif`, `solarized`, `blood`, `moon`, `night`, `black`, `league`, and `white`. And for the syntax highlighting style: `default`, `tango`, `pygments`, `kate`, `monochrome`, `espresso`, `zenburn`, and `haddock`. Pass null to prevent syntax highlighting. The way to specify it is the same than the previous presentation types.



# Slide with Bullets

\pause

- Bullet 1
- Bullet 2
- Bullet 3

# Slide with Numerical Bullets

1. Bullet 1
2. Bullet 2
3. Bullet 3

# Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```


# Slide with Table

```{r table}
knitr::kable(summary(cars), row.names = FALSE)
```


# Slide with Plot

```{r pressure}
plot(pressure)
```

# Two Columns

:::::::::::::: {.columns}
::: {.column}
contents of the left column
:::
::: {.column}
contents of the right column
:::
::::::::::::::


# Slide with Equation

$$
\frac{-b \pm \sqrt{b^2 - 4ac}}{2a}
$$

# Reference
